---
title: "DGM"
author: "Megha Joshi"
date: "5/27/2022"
output:
  html_document:
    toc: true
    toc_float: true
    number_sections: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, warning = F, message = F}
library(tidyverse)
library(lme4)
library(performance)
```

# DGM 

```{r}
source("01_dgm_function.R")

generate_data
```


# Params

```{r}
# memory exhaustion if I try to make all of these large 
# for checking the distributions - need to increased the numbers here
k <- 1000 #schools
j <-20  # teachers 
i <- 10 # students

icc3 <- 0.05  # icc for school 
icc2 <- 0.20 # icc for teachers
R2 <- .40


ps_coef <- matrix(c(.07, 0.8, -0.25, 0.6, -0.4, 1, 1))  #what values for pi 6 and 7 in the notes?
pr_star <- .5

outcome_coef <- matrix(c(1, 0.3, .5, .4, -0.2, 1, 1))

delta <- -0.4
```


# Generate Data

```{r}
set.seed(20210527)

example_dat <- generate_data(k = k,
                             j = j, 
                             i = i, 
                             icc3 = icc3, 
                             icc2 = icc2, 
                             R2 = R2,
                             ps_coef = ps_coef, 
                             pr_star = pr_star, 
                             outcome_coef = outcome_coef, 
                             delta = delta)
```


# Examine data
  
## Missingness

```{r}
# check if any is missing 
map(example_dat, ~ sum(is.na(.)))
```


## Proportion in Treatment

```{r}
# proportion depends on the value of the intercept in ps model
# so not sure what pr_star is doing
prop.table(table(example_dat$D))
```


## Distributions

### School level covariate

```{r}
school_cov_dat <- 
  example_dat %>%
  select(school_id, Z_k) %>%
  distinct(.)

ggplot(school_cov_dat, aes(x = Z_k)) +
  geom_density() + 
  theme_minimal()

mean(school_cov_dat$Z_k)
sd(school_cov_dat$Z_k)
```


### Teacher level covariate

```{r}
teacher_cov_dat <- 
  example_dat %>%
  select(teacher_id, W_jk) %>%
  distinct(.)

ggplot(teacher_cov_dat, aes(x = W_jk)) +
  geom_density() + 
  theme_minimal()

mean(teacher_cov_dat$W_jk)
sd(teacher_cov_dat$W_jk)
```

### Student level covariate

```{r}
ggplot(example_dat, aes(x = X_ijk)) +
  geom_density() + 
  theme_minimal()

mean(example_dat$X_ijk)
sd(example_dat$X_ijk)

ggplot(example_dat, aes(x = U_ijk)) +
  geom_density() + 
  theme_minimal()

mean(example_dat$U_ijk)
sd(example_dat$U_ijk)
```


## Check Model Params

### Coefficients

```{r}
out_mod <- lmer(Y_ijk ~ D  + X_ijk + W_jk + Z_k + 
                    (1 | school_id/teacher_id),
                  data = example_dat)

summary(out_mod)
```

Compare to the coefficients used in data gen:

```{r}
tibble(vars = c("intercept", "X_ijk", "U_ijk", 'W_jk', "Z_k", "r_k", "u_jk"),
         params = as.vector(outcome_coef))

delta
```


### ICC 

Calculating ICC from performance package:

```{r}
performance::icc(out_mod)
```

Breaking it down by group. ICC for teacher id x school id?

```{r}
performance::icc(out_mod, by_group = TRUE)
```

The icc's used in the dgm:

```{r}
icc3 # school level 
icc2 # teacher level 
```

These match the iccs.

This is the sd of the residual at school level:

```{r}
sd(example_dat$r_k)
```

This is the sd of the residual at teacher level:


```{r}
sd(example_dat$u_jk)
```

